Constant Partying: \\ Introducing a Generic Toolkit for Recursive Partitioning in R

### 2014-03-19 pkg/partykit/inst/NUS-2014/constparty.Rnw
remove fixme
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@504 255f4249-2263-4417-b1ea-8498779e27a7
final
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@506 255f4249-2263-4417-b1ea-8498779e27a7

\begin{frame}
\frametitle{findsplit}

R code

@@

\begin{frame}
\frametitle{growtree}

R code

@@

\begin{frame}
\frametitle{mytree}

R code

@@

All examples have been produced with
R~\Sexpr{with(R.Version(), paste(major, minor, sep = "."))} and packages
\begin{itemize}
\item partykit~\Sexpr{packageDescription("partykit")$Version},
\item rpart~\Sexpr{packageDescription("rpart")$Version},
\item  RWeka~\Sexpr{packageDescription("RWeka")$Version},
\item evtree~\Sexpr{packageDescription("evtree")$Version}. 
\end{itemize}
All packages are
freely available under the GPL from \url{http://CRAN.R-project.org/}.

FIXME: partykit still only on R-Forge

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package vignette version~0.8-0.
 URL~\url{http://CRAN.R-project.org/package=partykit}

>>>>

\begin{frame}[fragile]
\frametitle{findsplit}

\begin{Schunk}
\begin{Sinput}
findsplit <- function(response, data, weights) {
  ### response: name of the response variable   
  ### data: data.frame with all variables
  ### weights: case weights for current node

  ### ... some computations

  ### return split as partysplit object
  return(partysplit(
      varid = as.integer(xselect),         ### which variable?
      index = levels(data[[xselect]]) %in%
              splitpoint + 1L,             ### which split point?
      info = list(p.value = exp(logpmin)   ### save p-value
  )))
}
\end{Sinput}
\end{Schunk}

@@

\begin{frame}[fragile]
\frametitle{growtree}

\begin{Schunk}
\begin{Sinput}
growtree <- function(id = 1L, response, data, weights) {
  ### recursive function of
  ### id: node identifier
  ### response: name of the response variable 
  ### data: data.frame with all variables 
  ### weights: case weights for current node

  ### ... some computations, call to findsplit()
  ### and growtree()

  ### return nodes  
  return(partynode(id = as.integer(id), split = sp, kids = kids))
}
\end{Sinput}
\end{Schunk}

@@

\begin{frame}[fragile]
\frametitle{mytree}

\begin{Schunk}
\begin{Sinput}
mytree <- function(formula, data, weights = NULL) {
  ### formula: a model formula
  ### data: data.frame with all variables 
  ### weights: case weights for root node

  ### ... some computations

  nodes <- growtree(id = 1L, response, data, weights)

  ### ... some computations

  ### return rich constparty object
  ret <- party(nodes, data = data,
    fitted = data.frame(
      "(fitted)" = fitted,
      "(response)" = data[[response]],
      "(weights)" = weights,
      check.names = FALSE), 
    terms = terms(formula)) 
  as.constparty(ret)
}  
\end{Sinput}
\end{Schunk}

@@

All examples have been produced with
R~\Sexpr{with(R.Version(), paste(major, minor, sep = "."))} and packages
\begin{itemize}
\item partykit~\Sexpr{packageDescription("partykit")$Version},
\item rpart~\Sexpr{packageDescription("rpart")$Version},
\item  RWeka~\Sexpr{packageDescription("RWeka")$Version},
\item evtree~\Sexpr{packageDescription("evtree")$Version}. 
\end{itemize}
All packages are
freely available under the GPL from \url{http://R-forge.R-project.org/} (partykit~\Sexpr{packageDescription("partykit")$Version})
or \url{http://CRAN.R-project.org/}.

@@

Hothorn T, Zeileis A (2014).
 \textit{partykit: A Toolkit for Recursive Partytioning.}
 R~package vignette version~0.8-0.
 URL~\url{https://r-forge.r-project.org/projects/partykit}
